### 2022-10-10 Papers/ICCC-2023/sections/abstract.tex
stuff

This paper proposes a new approach to compiler architecture that places the interpreter as the central component of the compiler.
Translation of user code into the executable form is done using an interpreted module, written in the target language, and uses the same data structures accessible to the programmer.
This boosts the flexibility and extensibility of the compiler and ensures the completness of the available metadata and the ability to execute any code at compile-time.

Compile Time Function Execution (CTFE) First pattern is designed with compiling low-level, non-garbage-collected, reflection-enabled languages in mind.
It was created in order to compile C-=-1, which aimed to allow the programmer to execute any code at compile time, as well as analyze and modify the program structure.
Thanks to the extensibility of the designed compiler, programs written in C-=-1 can also generate marshalling bindings for other languages and support a variety of unexpected programming paradigms.

The flexibility and extensibility of CTFE frist are offset by higher complexity of the compiler and rigidity of the data strctures used.
The interpreted module, which is a large component, is difficult to debug due to the additional indirection.
Since the programmer has access to the same data structures, used by the compiler, they are a part of the compiled languages standard library and backwards compability must be maitained.

>>>>

In this paper a new approach to compiler architecture that places the interpreter as the central component of the compiler.
Translation of user code into the executable form is done using an interpreted module, written in the target language, and uses the same data structures accessible to the programmer.
This boosts the flexibility and extensibility of the compiler and ensures the completness of the available metadata and the ability to execute any code at compile-time.

Compile Time Function Execution (CTFE) First pattern is designed with compiling low-level, non-garbage-collected, reflection-enabled languages in mind.
It was created in order to compile C-=-1, which aimed to allow the programmer to execute any code at compile time, as well as analyze and modify the program structure.
Grace to the extensibility of the designed compiler, programs written in C-=-1 can also generate marshalling bindings for other languages and support a variety of unexpected programming paradigms.

The flexibility and extensibility of CTFE frist are offset by higher complexity of the compiler and rigidity of the data strctures used.
The interpreted module, which is a large component, is difficult to debug.
Since the programmer has access to the same data structures, used by the compiler, they are a part of the compiled languages standard library and backwards compability must be maitained.

### 2022-10-10 Papers/ICCC-2023/sections/design.tex
stuff

C-=-1 type system heavily borrows from C++.
Program may contain user defined classes, with members which may have limited accessibility.
Generic programming is achieved by the use of templates, although they are mutch more limited than the ones present in C++.
The user may also use pointers to objects, with arbitrary indirection (for example pointer to pointer to object).
Additionally, the language contains the concept of an \lstinline{interface}, similar to the one found in C\#.

@@

An important consideration with implementing a CTFE First compiler, is what limitations to put on modifications of user code.
Depending on language design, it may be possible to introduce circular references between the functions that modify the codebase.
For example if function \lstinline{A} is modified by function \lstinline{B} and \lstinline{B} invokes \lstinline{A}, the behaviour of the program is unpredictable.
This problem will only be magnified by larger program sizes.

@@

The backend code must be invokable from within the interpreted program in the target language.
Depending on how the interpreter was designed, this can represent a significant undertaking.
Compiler backends are large and for the Compiler Interface to take advantage of them, they must be fully available.
This means exposing each function and type within the library, to the interpreted code.
These bindings could feasibly be generated automatically \cite{marshalling_auto_generation}, but this tehnique was not used when implementing C-=-1 compiler.

>>>>

C-=-1 type system heavily borrows from C++.
Program may contain user defined classes, with members which may have limited accessibility.
Generic programming is achieved by the use of templates, although they are much more limited than the ones present in C++.
The user may also use pointers to objects, with arbitrary indirection (for example pointer to pointer to object).
Additionally, the language contains the concept of an \lstinline{interface}, similar to the one found in C\#.

@@

An important consideration with implementing a CTFE First compiler, is what limitations to put on modifications of user code. %todo: longer
Depending on language design, it may be possible to introduce circular references between the functions that modify the codebase.
For example if function \lstinline{A} is modified by function \lstinline{B} and \lstinline{B} invokes \lstinline{A}, the behaviour of the program is unpredictable.
This problem will only be magnified by larger program sizes.

@@

The backend code must be invokable from within the interpreted program in the target language.
Depending on how the interpreter was designed, this may require significant effort. %todo: maybe other word
Compiler backends are large and for the Compiler Interface to take advantage of them, they must be fully available.
This means exposing each function and type within the library, to the interpreted code.
These bindings could feasibly be generated automatically \cite{marshalling_auto_generation}, but this tehnique was not used when implementing C-=-1 compiler.

### 2022-10-10 Papers/ICCC-2023/sections/introduction.tex
stuff

This paper proposes a new approach to compiler construction that places Compile Time Function Execution capabilities as the first priority.
This architecture is called CTFE First.
CTFE First builds the compiler around the interpreter component.
The role of the compiler is to construct the semantic model of the program being compiled and pass it as data to the interpreted Compiler-Intreface module.
Compiler-Interface then tranforms the model into the backend's assembly language to be compiled to executable.
The design of the language that sparked this approach was described in chapter \ref{language-design}.
Chapter \ref{compiler-design} deals with structure of a CTFE First compiler and how its components interact.

Using CTFE First approach carries with it certain unique implementation considerations.
Data structures used within the compiler and the way that the program is modeled is tightly coupled with the compiled language.
These challenges, as well as how they were solved in C-=-1 compiler were described in chapter \ref{implementation}.

>>>>

In this paper a new approach to compiler construction that places Compile Time Function Execution capabilities as the first priority is proposed.
This architecture is called CTFE First.
CTFE First builds the compiler around the interpreter component.
The role of the compiler is to construct the semantic model of the program being compiled and pass it as data to the interpreted Compiler-Intreface module.
Compiler-Interface then tranforms the model into the backend's assembly language to be compiled to executable.
The design of the language that motivated this approach was described in chapter \ref{language-design}.
Chapter \ref{compiler-design} deals with structure of a CTFE First compiler and how its components interact.

Using CTFE First approach carries with it certain unique implementation considerations.
Data structures used within the compiler and the way that the program is modeled is tightly coupled with the compiled language.
These challenges, as well as how they were solved in C-=-1 compiler are described in chapter \ref{implementation}.
